---
title: "Coursework"
format: html
editor: visual
---

# 3 | Multiple Linear Regression

## 3.1 | Statistical Data Analysis

In this lab, I needed to find a 'good' model to estimate the volume growth per hectare (i.e., the response variable) of upland Canadian boreal forests in southeast Canada, using three predictor variables including the basal area per hectare, the percentage of the basal area in black spruce, and the stand site index for the dominant species. First, I explored the dataset using summary statistics and scatterplots to gain a more in-depth understanding of how these variables relate to each other. This step helped identify patterns and potential relationships (e.g., a positive correlation between VOL_growth and BA).

```{r, echo=FALSE, fig.width=10, fig.height=8}
# Import dataset
A3data <- read.csv("D:/Github/E-Portfolio_KelvinLee/Maps_Kelvin/A3.csv", header = TRUE, sep = ",")

# Summary statistics
summary(A3data)

# Scatterplot matrix to explore relationships
pairs(~ VOL_growth + BA + perBA_spruce + SI,
      data = A3data,
      main = "Scatterplot Matrix for Forest Growth Variables")
```

\*Volume growth per hectare (VOL_growth), basal area per hectare (BA), percent of basal area in black spruce (perBA_spruce) & stand site index for the dominant species (SI)

## 3.2 | Regression Modelling and Feature Engineering

Afterward, I attempted to build several multiple linear regression models to explain VOL_growth with various predictor variables. The model displayed below uses transformed BA and perBA_spruce (e.g., log and squared terms), which can make nonlinear regression relationship more linear and enhance model performance.

The regression model was highly significant (F = 151.3, p \< 0.001) and explained 92.37% of the variation in VOL_growth (Adjusted R² = 0.9176). Both logBA and perBA_sprucesq were significant predictors (p \< 0.001). In short, logBA and perBA_sprucesq greatly influence VOL_growth.

```{r, echo=FALSE, fig.width=10, fig.height=8}
# Create transformed variables
A3data$logBA <- log(A3data$BA)
A3data$perBA_sprucesq <- A3data$perBA_spruce^2

# Fit linear regression model
model.3 <- lm(VOL_growth ~ logBA + perBA_sprucesq, data = A3data)

# Model results
summary(model.3)

# ANOVA for model evaluation
anova(model.3)
```

## 3.3 | Model Diagnostics and Predictive Analysis

I evaluated the models by examining residual and QQ plots and performing a Shapiro–Wilk test, to verify whether the regression assumptions (e.g. linearity, normality, homoscedasticity and independence) were satisfied. Model 3, which performed best, was selected to generate predictions and confidence intervals for new observations. This model predicts a volume growth of approximately 2.32 m³/ha, with a true mean value likely falling between 2.23 and 2.40 m³/ha at 95% confidence.

```{r, echo=FALSE, fig.width=10, fig.height=8}
# Predicted values and residuals
A3data$yhat.3 <- fitted(model.3)
A3data$resid.3 <- resid(model.3)
A3data$stdresid.3 <- resid(model.3)/summary(model.3)$sigma

# Residual diagnostic plot
plot(resid.3 ~ yhat.3, data = A3data,
     xlab = "Predicted VOL_growth",
     ylab = "Residuals",
     main = "Residual Plot",
     pch = 19)
abline(a = 0, b = 0, col = "red")

# Normality check (QQ plot)
qqnorm(A3data$stdresid.3)
qqline(A3data$stdresid.3, col = "red")

# Shapiro-Wilk normality test
shapiro.test(A3data$stdresid.3)

# Prediction for new observation
new <- data.frame(logBA = log(19.2),
                  perBA_sprucesq = 92^2)

predict(model.3, new, interval = "confidence", level = 0.95)
```
