---
title: "Community Project"
format: html
editor: visual
---

# 2 | Disaster Response Mapping

The aim of this project is to create an interactive map that is readily operable and accessible for Mudge Island residents and volunteers, particularly non-GIS users, in both online and offline circumstances. I set up a free QField account that people can use to update and review the map on their computers or phones anytime, anywhere. Map users can click to access the information they need, such as the precise location of water caches and evacuation points by boat or helicopter. This interactive map has proven invaluable in wildfire response decision-making and enhancing familiarity with the island's environment. The map below is just a demo to show the map's potential.

```{r DRM-leaflet, include = FALSE}
library(terra)
library(raster)  # for Leaflet compatibility
library(leaflet)

## --- Map view defaults -------------------------------------------------------
mudge_lng <- -123.7910
mudge_lat <-  49.1290
zoom_lvl  <- 14

## --- Load rasters ------------------------------------------------------------
hill   <- rast("Maps_Kelvin/Hillshade.tif")
slope  <- rast("Maps_Kelvin/Slope.tif")
aspect <- rast("Maps_Kelvin/Aspect.tif")

## --- Load vectors ------------------------------------------------------------
parcel  <- vect("Maps_Kelvin/Parcel.gpkg")  # use the fixed GeoPackage
roads   <- vect("Maps_Kelvin/Roads.gpkg")
water   <- vect("Maps_Kelvin/WaterStorage.gpkg")
access  <- vect("Maps_Kelvin/AccessPoints.gpkg")
address <- vect("Maps_Kelvin/AddressPoints.gpkg")

## --- Reproject everything to lat-long (WGS84) --------------------------------
target_crs <- "EPSG:4326"

hill    <- project(hill,    target_crs)
slope   <- project(slope,   target_crs)
aspect  <- project(aspect,  target_crs)

parcel  <- project(parcel,  target_crs)
roads   <- project(roads,   target_crs)
water   <- project(water,   target_crs)
access  <- project(access,  target_crs)
address <- project(address, target_crs)

## --- Hillshade reclassification ---------------------------------------------
hill <- classify(hill, matrix(c(
   1,  85, 1,
  85, 170, 2,
 170, 255, 3
), ncol = 3, byrow = TRUE))

levels(hill) <- data.frame(
  value = 1:3,
  label = c("Low illumination", "Medium illumination", "High illumination")
)

## --- Slope reclassification --------------------------------------------------
slope <- classify(slope, matrix(c(
   0,   5, 1,
   5,  15, 2,
  15,  30, 3,
  30,  60, 4,
  60, Inf, 5
), ncol = 3, byrow = TRUE))

levels(slope) <- data.frame(
  value = 1:5,
  label = c("Flat", "Gentle", "Moderate", "Steep", "Very Steep")
)

## --- Aspect reclassification -------------------------------------------------
aspect <- classify(aspect, matrix(c(
   0,  45, 1,
  45,  90, 2,
  90, 135, 3,
 135, 180, 4,
 180, 225, 5,
 225, 270, 6,
 270, 315, 7,
 315, 360, 1
), ncol = 3, byrow = TRUE), include.lowest = TRUE)

levels(aspect) <- data.frame(
  value = 1:7,
  label = c(
    "North", "Northeast", "East", "Southeast",
    "South", "Southwest", "West"
  )
)

## --- Color palettes ----------------------------------------------------------
hill_cols   <- c("#2b2b2b", "#7f7f7f", "#d9d9d9")
slope_cols  <- c("#edf8fb","#b2e2e2","#66c2a4","#2ca25f","#006d2c")
aspect_cols <- c("#2b004f","#3b2b8f","#2f5fb3","#2fa4a9",
                 "#33c27d","#7cd250","#c7e75b")

## --- Convert rasters to 'raster' objects for Leaflet ------------------------
hill_raster   <- raster(hill)
slope_raster  <- raster(slope)
aspect_raster <- raster(aspect)

## --- Create Leaflet map ------------------------------------------------------
m <- leaflet(options = leafletOptions(preferCanvas = TRUE)) %>%
  
  addProviderTiles("Esri.WorldImagery", group = "Basemap") %>%
  
  ## --- Raster layers ---
  addRasterImage(hill_raster, colors = hill_cols, opacity = 0.80, group = "Hillshade") %>%
  addRasterImage(slope_raster, colors = slope_cols, opacity = 0.80, group = "Slope") %>%
  addRasterImage(aspect_raster, colors = aspect_cols, opacity = 0.80, group = "Aspect") %>%
  
  ## --- Vector layers ---
  addPolygons(
    data = parcel,
    fill = FALSE,
    color = "white",
    weight = 1,
    popup = ~paste0(
      "<b>PID:</b> ", PID_FORMATTED, "<br>",
      "<b>Parcel Name:</b> ", PARCEL_NAME, "<br>",
      "<b>Municipality:</b> ", MUNICIPALITY
    ),
    group = "Parcels"
  ) %>%
  
  addPolylines(
    data = roads,
    color = "yellow",
    weight = 2,
    popup = ~paste0(
      "<b>Road:</b> ", ROAD_NAME_FULL, "<br>",
      "<b>Class:</b> ", ROAD_CLASS
    ),
    group = "Roads"
  ) %>%
  
  addCircleMarkers(
    data = water,
    radius = 6,
    color = "cyan",
    fillOpacity = 0.9,
    popup = ~paste0(
      "<b>Name:</b> ", Name, "<br>",
      "<b>Description:</b> ", description
    ),
    group = "Water Storage"
  ) %>%
  
  addCircleMarkers(
    data = access,
    radius = 5,
    color = "orange",
    popup = ~paste0(
      "<b>Access Type:</b> ", AccessType, "<br>",
      "<b>Location:</b> ", Location
    ),
    group = "Access Points"
  ) %>%
  
  addCircleMarkers(
    data = address,
    radius = 4,
    color = "blue",
    popup = ~paste0(
      "<b>Address:</b> ", ADDRESS, "<br>",
      "<b>Road:</b> ", ROAD
    ),
    group = "Address Points"
  ) %>%
  
  ## --- Layer control ---
  addLayersControl(
    overlayGroups = c(
      "Hillshade", "Slope", "Aspect",
      "Parcels", "Roads", "Water Storage",
      "Access Points", "Address Points"
    ),
    options = layersControlOptions(collapsed = FALSE)
  ) %>%
  
    ## --- Legends (auto-toggle with layers) ------------------------------------
  addLegend(
    position = "bottomright",
    colors = hill_cols,
    labels = levels(hill)[[1]]$label,
    title  = "Hillshade",
    opacity = 0.8,
    group = "Hillshade"
  ) %>%
  
  addLegend(
    position = "bottomright",
    colors = slope_cols,
    labels = levels(slope)[[1]]$label,
    title  = "Slope",
    opacity = 0.8,
    group = "Slope"
  ) %>%
  
  addLegend(
    position = "bottomright",
    colors = aspect_cols,
    labels = levels(aspect)[[1]]$label,
    title  = "Aspect",
    opacity = 0.8,
    group = "Aspect"
  ) %>%
  
  ## --- Hide raster layers by default ---
  hideGroup(c("Hillshade", "Slope", "Aspect")) %>%
  
  addScaleBar(position = "bottomleft") %>%
  
  ## --- Zoom to Mudge Island coordinates ---
  setView(lng = mudge_lng, lat = mudge_lat, zoom = zoom_lvl)
```

```{r DRM-map, echo=FALSE}
m
```